Time for a rethink: time sub-sampling methods in disparity-through-time analyses

### 2018-02-12 manuscript/time-slice.tex
Fix dryad refs and minor edits

\subsection{Example datasets}
\label{datasets}
To test the different time binning/slicing methods we selected four datasets: a mammal dataset from \cite{beckancient2014}, two theropod datasets from \cite{brusatte2014gradual} and \cite{bapst2016topology}, and a crinoid dataset from \cite{wright2017bayesian}.
Table \ref{table:datasets} and the Supporting Information Appendix S1 provide more details. 
%TG: TODO: I can't find the Table in Word format anymore. We have to make sure the dates are correct. 
Each dataset consists of first and last occurrence dates for all taxa, a matrix of morphological characters in NEXUS format, and a time-scaled phylogeny. 
These datasets are freely available with their accompanying papers (Table \ref{table:datasets}), but for reproducibility purposes we also provide the data we used on GitHub (\url{https://github.com/nhcooper123/time-slice/data}).

@@

\begin{figure}[!htbp]
    \centering
    %\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/Figure2-binning.pdf}
    \caption[Outline of the three time sub-sampling methods]
    {Outline of the three time sub-sampling methods. 
    Stratigraphy: time sub-samples are defined by stratigraphic periods.
    Here there are five stratigraphic periods in the 20 MY (million years) time frame of interest, i.e. five bins/slices with variable sizes/intervals.
    Duration: time sub-samples are defined based on the mean duration of stratigraphic periods in the time frame of interest. 
    Here, the mean duration of stratigraphic periods is 5 MY, so there are four bins/slices of 5 MY duration (or four slices with 5 MY intervals between them) in the 20 MY time frame of interest. 
    Number: time sub-samples are defined based on the number of stratigraphic periods in the time frame of interest. 
    Here, there are five stratigraphic periods, so there are five bins/slices of 4 MY duration (or five slices with 4 MY intervals between them) in the 20 MY time frame of interest.}
    \label{fig:bins}
\end{figure}

@@

\section{Data archiving statement}
Data for this study are available from \cite{dryad_n2g80,dryad_6hb7j,dryad_84t75,beckancient2014} but for ease of reproducibility can also be found on GitHub (\url{https://github.com/nhcooper123/time-slice/data}). % add proper link to zenodo
Supporting information can be found on Dryad at % Add Dryad link

\section{Supporting information}
Additional Supporting information can be found on Dryad at:\\
Appendix S1: Extra details of datasets. \\
Appendix S2: Additional figures. \\
Appendix S3: Additional tables.

>>>>

\subsection{Example datasets}
\label{datasets}
To test the different time binning/slicing methods we selected four datasets: a mammal dataset from \cite{beckancient2014}, two theropod datasets from \cite{brusatte2014gradual} and \cite{bapst2016topology}, and a crinoid dataset from \cite{wright2017bayesian}.
Table \ref{table:datasets} and the Supporting Information Appendix S1 provide more details. 
Each dataset consists of first and last occurrence dates for all taxa, a matrix of morphological characters in NEXUS format, and a time-scaled phylogeny. 
These datasets are freely available with their accompanying papers (Table \ref{table:datasets}), but for reproducibility purposes we also provide the data we used on GitHub (\url{https://github.com/nhcooper123/time-slice/data}).

@@

\begin{figure}[!htbp]
    \centering
    %\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/Figure2-binning.pdf}
    \caption[Outline of the three time sub-sampling methods]
    {Outline of the three time sub-sampling methods. 
    Stratigraphy: time sub-samples are defined by stratigraphic periods.
    Here there are five stratigraphic periods in the 20 My (million years) time frame of interest, i.e. five bins/slices with variable sizes/intervals.
    Duration: time sub-samples are defined based on the mean duration of stratigraphic periods in the time frame of interest. 
    Here, the mean duration of stratigraphic periods is 5 My, so there are four bins/slices of 5 My duration (or four slices with 5 My intervals between them) in the 20 My time frame of interest. 
    Number: time sub-samples are defined based on the number of stratigraphic periods in the time frame of interest. 
    Here, there are five stratigraphic periods, so there are five bins/slices of 4 My duration (or five slices with 4 My intervals between them) in the 20 My time frame of interest.}
    \label{fig:bins}
\end{figure}

@@

\section{Data archiving statement}
Data for this study are available from \cite{dryad_n2g80,dryad_6hb7j,dryad_84t75,beckancient2014} but for ease of reproducibility can also be found on GitHub (\url{https://github.com/nhcooper123/time-slice/data}). % add proper link to zenodo
Supporting information can be found on Dryad at https://doi.org/10.5061/dryad.vp4q518 \cite{data-time-slice}.

\section{Supporting information}
Additional Supporting information can be found on Dryad at: https://doi.org/10.5061/dryad.vp4q518 \cite{data-time-slice}.\\
Appendix S1: Extra details of datasets. \\
Appendix S2: Additional figures. \\
Appendix S3: Additional tables.
